---
title: "Brian McNitt Lab 3"
output:
  html_document: default
---

### 1. Quick Summary

1. Import Advertising.csv to R and save it as a data frame named Ad. Provide the names of the variables in Ad and their summary statistics.  


```{r}
Ad<-read.csv("Advertising.csv")
Ad<-Ad[-1]
summary(Ad)
```

Our variable names TV, Radio, newspaper, and sales. Above displays their min, 1 quartile, median, mean, 3rd quartile

###2.	Simple Linear Regression
a.	Provide the regression result. 
b.	Is there a relationship between sales and TV advertising budget? Why? 
c.	How strong is the relationship between sales and TV advertising budget? 
d.	Does TV advertising budget affect sales? How?
e.	How large is the effect of each medium on sales? (Hint: use the confint() function to calculate the 95% confidence interval of the coefficient estimate.)?? multiple regression?
f.	If we have a TV advertising budget of $100,000, what is the prediction of sales? (Hint: use the predict() function.)

```{r}
lm1.fit=lm(sales~TV, data=Ad)

summary(lm1.fit) 
```

B:) There is a relationship between sales and TV adertising budget. Tthe p-value for the coefficient is less than .001. At 95% confidence we can reject the null hypthesis that the coefficient has 0 effect, and conclude that it does have an effect on the dependent variable.

C:) The relationship between sales and TV advertising is fairly strong. The adjusted R-squared value is ~ .61, meaning 61% of the of the variance of Sales can be explained by the variance in TV Advertising.

D:) TV advertising effects sales in the following: for every 1 unit increase in TV Advertising, sales on average tends to increase by .047 units.

```{r}

confint(lm1.fit)
```


E:) We are 95% confident that for every 1 unit increase in the X variable, sales increases within the lower and upper bounds printed above.

F:)

```{r}

## note we fit the model based on Advertising Budget units of measurement in ****
predict(lm1.fit, 
        data.frame(TV=c(100)), interval="confidence")
```

 If we have a TV advertising budget of $100,000, the prediction of sales is ~11.78 unts


###3. Multiple Regression
a)	Provide the regression result. 
b)	Is there a relationship between sales and advertising budgets? Why?
c)	How strong is the relationship between advertising budgets and sales? 
d)	Which media contribute to sales? 
e)	How does this model compare to the simple linear regression model of Sales on TV? Which one would you choose? Why?
f)	How large is the effect of each medium on sales?
g)	If we have TV, radio, and newspaper advertising budgets of $100,000, $20,000, and $30,550, respectively, what is the prediction of sales? 

```{r}
lm2.fit=lm(Ad$sales~., data=Ad)
summary(lm2.fit)
```

B:) We can conclude that there is relationship between advertising budgets and sales because the p-value of the regression model is < .05. Meaning at 95% confidence, we can reject the null hypthothesis that there is 0 relationship between advertising budgets and sales, and conclude that there is in fact a relationship. 

C:) The relationship between advertising budgets and Sales is strong. The adjusted R-squared value is ~ .89, meaning 89% of the of the variance of Sales (Y) can be explained by the variance in advertising budgets (X's).

D:) There is a relationship between the TV and Radio advertising budgets and Sales because their p-values are less than .05. The only variable we cannot say effects Sales is newspaper budget because its p-value is .86.

E:) The multiple linear regression model is a stronger predictor of sales than the simple linear regression. To evalulate the models, we can compare them using adjusted R-squared. The model with the higher R-squared value is stronger. I would choose the multiple regression model. 

```{r}
confint(lm2.fit)
```

F:) 

```{r}
predict(lm2.fit, data.frame(TV=c(100),
                            radio=(20),
                            newspaper=(30.55)), interval="confidence")
## ORDER matters, tv, radio, newspaper

```



